Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-11-14 docs/00-manuscripts/mdpi/manuscript.tex
revised conclusion

This study analyzed defoliation of trees in northern Spain by using hyperspectral data as input for ML models which used hyperparameter tuning and filter-based feature selection.
Substantial differences in performance occurred depending on which feature selection and machine learning methods were combined.
SVM showed the most robust behavior across all highly\ correlated datasets and was able to predict the response variable of this study substantially better than other methods.

>>>>

This study analyzed the effectiveness of filter-based feature selection in improving various machine-learning models of defoliation of trees in northern Spain based on hyperspectral remote-sensing data.
Substantial differences in performance occurred depending on which feature-selection and machine-learning methods were combined.
SVM showed the most robust behavior across all highly\ correlated datasets and was able to predict the response variable of this study substantially better than other methods.
